How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-14 research/paper/draft.tex
periodic commit

The directed acyclic graph of Fig. \ref{fig:pgm} represents a probabilistic 
graphical model for hierarchical inference of $n(z)$, the mathematical 
interpretation of which will be presented below.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{\textbf{Replace \texttt{daft} version with more 
polished \texttt{tikz} version.}}
	\label{fig:pgm}
	\end{center}
\end{figure}

\textbf{Math from \texttt{prob-z} version will go here.}

>>>>

We present the two attributes of a probabilistic graphical model (PGM) for the 
redshift distribution $n(z)$: the directed acyclic graph of Fig. \ref{fig:pgm} 
and its mathematical interpretation below.  The assumption underlying the 
concept of photo-$z$ estimation is that each galaxy $i$ has some observed 
photometric data $\vec{d}_{i}$ (fluxes, magnitudes, or colors) that is drawn 
from a function of its redshift $z_{i}$, which is a parameter in this model.  
The redshifts $\{z_{i}\}$ for all galaxies in a survey are random draws from 
the redshift distribution, a function which itself may be parametrized by 
hyperparameters comprising $\vec{\phi}$ that are shared among all $N$ galaxies 
in the survey.  From this perspective, $n(z)$ is itself a probability 
distribution for galaxy redshifts, i.e. $z_{i} \sim n(z)$.  Given a functional 
form of $n(z)$, we can say $n(z) = p(z_{i}|\vec{\phi})$ for any $i = 1, \dots, 
N$, determining that $n(z)$ is in particular a likelihood.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{This directed acyclic graph corresponds to a PGM for a 
hierarchical inference of $p(\vec{\phi}|\{\vec{d}_{i}\})$.  In this graph, all 
random variables are shown in circles, with observed random variables shown in 
shaded circles.  Relationships between variables are indicated by arrows from 
parameters to the variables distributed according to functions of them.  The 
box indicates that there are a number of copies of the relationships between 
boxed parameters, each independent of all others.  The hyperparameters 
comprising $\vec{\phi}$, which define $n(z)$, are at the top.  Independently 
drawn from a function of the hyperparameters $\vec{\phi}$ are galaxy redshifts 
$\{z_{i}\}$ below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in 
shaded circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}

It would be easy to estimate $\vec{\phi}$ given $\{z_{i}\}_{N}$, however, what 
we actually have is photometric data $\{\vec{d}_{i}\}_{N}$ which we used to 
derive photo-$z$ PDFs.  Because a photo-$z$ PDF is a probability distribution 
conditioned on the photometric data, it must be interpreted as a posterior 
probability distribution.

In addition to the data, the posterior probability distribution is conditioned 
on other information about how it was made, which is in general specific to the 
method that produced it.  This information only influences the posterior by its 
implicit distribution over redshifts, which we call the interim prior over 
redshift.  The interim prior, like the redshift distribution we wish to infer, 
has some functional form with some parameters, but since the redshift 
distribution and interim prior need not share the same parametrization, we will 
use $\vec{\alpha}$ to represent the parameters for the interim prior.  Thus, 
the posterior probability that is often oversimplified as "$p(z_{i})$" is 
really the interim posterior probability $p(z_{i} | \vec{d}_{i}, 
\vec{\alpha})$.  Note that we will assume that all galaxies whose photo-$z$ 
interim posteriors are derived by a single method share the same interim prior 
$p(z | \vec{\alpha})$; depending on the method, this may not always be true.

Given a catalog of photo-$z$ interim posteriors $\{p(z_{i} | \vec{d}_{i}, 
\vec{\alpha})\}$

To make use of the photo-$z$ interim priors, it is absolutely essential that 
$\vec{\alpha}$ be known.
